---
title: "Stories From Superset Models"
author: "Jeremy Forbes"
date: "11/09/2018"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
load("Clean-Data/data_mod.rda")
load("Clean-Data/all_coefs.rda")
load("Clean-Data/change_coef_all.rda")

knitr::opts_chunk$set(echo = FALSE, results = FALSE)
```

# Significance of all coefficients

```{r}
all_coefs %>% 
  filter(term != "(Intercept)") %>% 
  ggplot(aes(x = year, y = estimate)) + 
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12))
```

Of particular interest:

- CurrentlyStudying and Educ - would expect similar effects

- Extractive - jump in 2010

- Unemployed - change from Labor to insignificant

- OtherLanuageHome - expect to be strong relationship, but is insignificant

# Stories from the data

## Education and Students

```{r}
all_coefs %>% filter(term %in% c("CurrentlyStudying", "Educ")) %>% 
  ggplot(aes(x=year, y=estimate)) +
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  facet_wrap(~term) +
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against CurrentlyStudying
data_mod %>% ggplot(aes(x = CurrentlyStudying, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year) + ggtitle("CurrentlyStudying")

data_mod %>% ggplot(aes(x = Educ, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year) + ggtitle("Educ")
```


```{r}
change_coef_all %>% 
  filter(term == "Educ") %>% 
  ggplot(aes(x=omitted_var, y=estimate)) + 
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = full_estimate), col = "blue", linetype = 2, alpha = 0.7) + 
  geom_hline(aes(yintercept = 0), col = "grey50") + 
  facet_wrap(~year) + 
  ggtitle(label = "Educ") +
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) 

change_coef_all %>% 
  filter(term == "CurrentlyStudying") %>% 
  ggplot(aes(x=omitted_var, y=estimate)) + 
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = full_estimate), col = "blue", linetype = 2, alpha = 0.7) + 
  geom_hline(aes(yintercept = 0), col = "grey50") + 
  facet_wrap(~year) + 
  ggtitle(label = "CurrentlyStudying") +
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) 
```
```{r}
data_mod %>% ggplot(aes(x=Educ, y=NoReligion)) + geom_point() + geom_smooth(method = "lm") + facet_wrap(~year)
data_mod %>% ggplot(aes(x=NoReligion, y=Perc_LNP)) + geom_point() + geom_smooth(method = "lm") + facet_wrap(~year)

```

Education policy has always been key policy issue in the weeks leading up to a federal election. The Labor party, more often than not, campaign with policies that boost funding for education, and the coalition will usually propose alternatives with less funding or aim to match particular objectives - for example, the "Better Schools Plan" in 2013. It would be reasonable to expect that electorates with higher student populations, and to an extent higher education levels, would be inclined to support Labor *every* election. The raw data plots indicate that student population may have a negative effect on $TPP$, whereas education levels will be insignificant or slightly negative (with respect to the Liberal party). 

After adjusting for the other socio-demographics, we find that effect of education levels is dependent on the age profile of the electorate, and the number of single parent households. In every election, the effect of education is more negative in electorates with lower median ages, and also becomes more negative with higher incidence of single parent households. For electorates with an average age profile, and average frequency of single parent households, education was significantly negative in 2004 and 2007 elections, and insignificant in the others.

We model the effect of student populations to be dependent on rental and mortgage payments of the electorate.  In 2007, 2010 and 2013, higher student proportions significantly increased Liberal support in electorates with average rental and mortgage payments. The effect of student population became more (positively) significant in lower rent and loan payment areas in all elections - although still insignificant in 2001 and 2004. In all elections, student populations were insignificant in areas with high rental and loan payments. 

So why was our intuition misguided along with the conclusions from the raw data? Essentially, it is an issue of confounding effects. 

We re-fit the model by dropping a single variable (along with any of its interactions) and observe the change in coefficient for CurrentlyStudying - which we interpret as the marginal effect when RentLoan is fixed at its mean. By omitting MedianAge and the interaction between CurrentlyStudying and MedianAge, the coefficient decreases by a large amount. This is not surprising, because electorates with higher student populations will be younger and therefore these two variables are negatively correlated ($\rho = −0.683$). Similarly, the effect of omitting higher education levels is absorbed by CurrentlyStudying, causing a decrease in estimated coefficient.

What this is ultimately saying is that conclusion on the effect of larger student populations that are based on the raw data (or those driven by intuition) are confounded by the effects of age and levels of completed education. Once we adjust for these, we find that larger student populations were significantly associated with the Liberal party in the past four elections in areas at or below mean rent and loan prices. Otherwise, student populations do not affect party preference.


## Unemployment
```{r}
all_coefs %>% filter(term == "Unemployed") %>% 
  ggplot(aes(x=year, y=estimate)) +
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against Unemployed
data_mod %>% ggplot(aes(x = Unemployed, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
```

```{r}
change_coef_all %>% 
  filter(term == "Unemployed") %>% 
  ggplot(aes(x=omitted_var, y=estimate)) + 
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = full_estimate), col = "blue", linetype = 2, alpha = 0.7) + 
  geom_hline(aes(yintercept = 0), col = "grey50") + 
  facet_wrap(~year) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) 
```

Our model indicates that in the 2001, 2004 and 2007 elections, higher unemployment rates were linked with more support for the Labor party. Interestingly, in all of those elections the Liberal party was the incumbent party with John Howard as Prime Minister. From 2010 onwards, unemployment has not had a significant effect, which is not what we would expect from the raw data plots. If we omit "office jobs", the estimated coefficient of unemployment becomes more negative, but remains insignificant in these three elections. Omitting Incomes would increase the effect in favor of the Liberal party, and would make 2004 and 2007 estimates insignificant. 

Therefore, we conclude that the unemployment rate was a significant determinant in two-party preference for 2001, 2004 and 2007 elections, but has since become insignificant, after adjusting for other socio-demographics - contrary to expectations.

## Extractive

```{r}
all_coefs %>% filter(term == "Extractive") %>% 
  ggplot(aes(x=year, y=estimate)) +
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against Extractive
data_mod %>% ggplot(aes(x = Extractive, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
```

Even in the election before the mining boom began in 2002, areas with more people working in "extractive" industries (mining, gas, water, gas, waste, electricity and agriculture) were significantly more supportive of the coalition. Over the following two elections the two parties did not differ significantly in their policies on natural resources, and we our coefficient estimates do not change much relative to 2001 - remaining significantly positive.

In 2010, the Labor party proposed a 40% tax on "super profits" made from ‘the exploitation of Australia’s non-renewable resources’, which was heavily opposed by the Liberal party, who instead offered the Exploration Development Incentive. The mining sector, particularly in Western Australia, vehemently objected to Labor's policy, with Chamber of Minerals and Energy chief executive describing it as a "$\$9$ billion handbreak on the economy". Consequently, we see a huge jump in the effect of extractive jobs in 2010, with estimated coefficient increasing from $3.0$ to $6.28$ - becoming the largest main effect coefficient in the model. Following the end of the mining boom in 2012, the estimated coefficient drops but remains significantly positive in 2013 and 2016.

## Birthplace of population

The raw data indicates that areas with more immigrants from South or Eastern Europe should have a strong relationship with Labor support. Similarly, the effects of immigrants from the UK should have a weakly positive or insignificant relationship with support for the Liberal party. We find that these are both true in our models - Born_SE_Europe is significantly negative in all years, and Born_UK is only significant (and positive) in the 2007 and 2010 elections.

Therefore, we conclude that the distribution of birthplace within an electorate place has significant influence on the voting behaviour. 

## Age profile

As previously mentioned, an interaction between age and education is included in our model. We find that across all elections, the more highly education an electorate is, the effect of age becomes more positive on the two party preferred vote - in favor of the Liberal party. For areas with low levels of education, in all elections, the effect of age becomes insignificant.

This is what we expect from looking at the raw data, as "older" electorates appear to be more conservative.

## ManagerAdminClericalSales

We anticipate a positive relationship between “office jobs” and support for the Liberal party, based on the raw plots. We find a significantly positive relationship between ManagerAdminClericalSales and support for LNP across all years.

## No Religion

We do not anticipate that rates of atheism should have a significant effect on party preference, but we find that in 2010 and 2013 electorates with higher rates of atheism were aligned more with the Labor party. Although practically uncorrelated, without accounting for an electorate’s breakdown of job by industry, estimated effect of NoReligion will be biased downwards.

## OneParent_House

Labor often propose policies that benefit families, and particularly single parent families. The raw plots indicate that there may be a strong negative relationship between OneParent_House and support for the Liberal party. We find that this is true only for electorates with higher levels of education. For those with mean or lower education, single parent households have no effect on party preference (assuming mean Incomes). Incomes also impact the estimated effect of single parent households with the effect of OneParent_House on Liberal support being more negative for electorates with lower incomes.

## RentLoan

Up to 2007, electorate median rent and loan repayments did not have a significant impact on party preference, but in 2010 we see a shift. This shift is dependent on the student population. We see that from 2010, areas with low student populations are more affected by rental and loan payments - with higher repayments being associated with support for the Liberal party. As student populations increase, the effect becomes insignificant.

## Incomes

We may expect areas with higher income to be slightly affiliated with the Liberal party - which typically has policies of lower taxes for both individuals and businesses. Or we may believe that it will not have an effect at all, which the raw plots indicate. We find that the effect of Incomes depend on the proportion of single parent households. In electorates with fewer single parent households (at the mean rate or below), Incomes had a negative effect on Liberal in all but 2001. In areas with higher incidence of single parent households, Incomes have no effect.

## Summary 

This indicates that our initial thoughts on the effect education levels would have is being confounded by these other factors. We are not laying any causal claims here, but rather indicating that our expectations about aggregate behaviour can be simeltaneously determined by grouping characteristics together. Essentially, our intuitions are very susceptible to omitted variable bias!
