---
title: "Superset-Models"
author: "Jeremy Forbes"
date: "01/09/2018"
output: html_document
---

```{r}
library(tidyverse)
library(stringr)
knitr::opts_knit$set(root.dir = "/Users/Jeremy/Documents/R/Modelling-Elections")
knitr::opts_chunk$set(echo = FALSE)
load("./Clean-Data/data_mod.rda")
load("./Clean-Data/var_imp_all.rda")
load("./Clean-Data/std_coef_all.rda")
```

# Superset
Determined by Akaike weights (top 5)

```{r}
# Top 5 variables
superset_AW_vars <- var_imp_all %>% 
  group_by(year) %>% 
  top_n(n = 5, wt = sum_w) %>%
  ungroup() %>% 
  select(var, varname) %>% 
  unique()
```

Model-averaged coefficients top 5

```{r}
# Top 5 variables
superset_SC_vars <- std_coef_all %>% 
  group_by(year) %>% 
  top_n(n = 5, wt = abs(avg_coef)) %>%
  ungroup() %>% 
  select(var, varname)  %>% 
  unique()

```

Union of the two OR use AW superset and add Incomes and Unemployment, as we expect these to be important and interesting drivers.

```{r}
#superset <- bind_rows(superset_AW_vars, superset_SC_vars) %>% group_by(varname) %>% unique()
superset <- bind_rows(superset_AW_vars, 
                      var_imp_all %>% filter(varname %in% c("Incomes", "Unemployed"),
                                             year == "2016") %>% select(var, varname)) 
save(superset, file = "./Clean-Data/superset.rda")
```


# Choosing interactions
Models with no interactions
```{r}
fit_ss_16_noint <- lm(Perc_LNP ~ ., 
                data = data_mod %>% 
                  filter(year == "2016") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_13_noint <- lm(Perc_LNP ~ ., 
                data = data_mod %>% 
                  filter(year == "2013") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_10_noint <- lm(Perc_LNP ~ ., 
                data = data_mod %>% 
                  filter(year == "2010") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_07_noint <- lm(Perc_LNP ~ ., 
                data = data_mod %>% 
                  filter(year == "2007") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_04_noint <- lm(Perc_LNP ~ ., 
                data = data_mod %>% 
                  filter(year == "2004") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_01_noint <- lm(Perc_LNP ~ ., 
                data = data_mod %>% 
                  filter(year == "2001") %>% 
                  select(Perc_LNP, (superset$varname %>% as.character)))
```


Record p-value for F test adding a single interaction to each model
```{r}
interact_F <- function(fit) {
  data_model <- fit$model
  formula_part1 <- (fit$call %>% as.character())[2]
  
  x_names <- names(data_model)[which(names(data_model) != "Perc_LNP")]
  
  pvalues_F <- matrix(nrow = length(x_names), ncol = length(x_names)) %>% as.data.frame()
  colnames(pvalues_F) <- x_names
  
  pvalues_F <- pvalues_F %>% 
    mutate(interact_var1 = x_names)
  

  for (i in 1:length(x_names)) {
    
    for (j in 1:length(x_names)) {
      
      if (i > j) {
      new_int = paste0(x_names[i], sep = ":", x_names[j])  
        
      formula = paste0(formula_part1, sep = " + ", new_int)
      
      mod <- lm(formula, data_model)
      
      # LR Test
      LR <- lmtest::lrtest(fit, mod)
      pval <- LR$`Pr(>Chisq)`[2]
      
      pvalues_F[i,j] <- pval
      
      }
      
    }
    
  }
  
  pvalues_F <- pvalues_F %>% 
    gather(key = "interact_var2", value = "pvalue", -interact_var1) %>% 
    filter(!is.na(pvalue))
  
  return(pvalues_F)
}

int16 <- interact_F(fit_ss_16_noint) %>% mutate(year = "2016")
int13 <- interact_F(fit_ss_13_noint) %>% mutate(year = "2013") 
int10 <- interact_F(fit_ss_10_noint) %>% mutate(year = "2010") 
int07 <- interact_F(fit_ss_07_noint) %>% mutate(year = "2007") 
int04 <- interact_F(fit_ss_04_noint) %>% mutate(year = "2004") 
int01 <- interact_F(fit_ss_01_noint) %>% mutate(year = "2001") 

bind_rows(int01, int04, int07, int10, int13, int16) %>% 
  filter(pvalue < 0.01) %>% 
  group_by(interact_var1, interact_var2) %>% 
  summarise(n = n()) %>% 
  arrange(-n) 
```

We now add interactions to our model. The selection criteria is having an interaction that significantly improves the model in at least half of the elections (at the 1% significance level). We therefore add Educ:MedianAge, CurrentlyStudying:RentLoan, Educ:OneParent_House, Incomes:OneParent_House.


```{r}
fit_ss_16 <- lm(Perc_LNP ~ . + Educ:MedianAge + CurrentlyStudying:RentLoan + Educ:OneParent_House + Incomes:OneParent_House, 
                data = data_mod %>% 
                  filter(year == "2016") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_13 <- lm(Perc_LNP ~ . + Educ:MedianAge + CurrentlyStudying:RentLoan + Educ:OneParent_House + Incomes:OneParent_House, 
                data = data_mod %>% 
                  filter(year == "2013") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_10 <- lm(Perc_LNP ~ . + Educ:MedianAge + CurrentlyStudying:RentLoan + Educ:OneParent_House + Incomes:OneParent_House, 
                data = data_mod %>% 
                  filter(year == "2010") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_07 <- lm(Perc_LNP ~ . + Educ:MedianAge + CurrentlyStudying:RentLoan + Educ:OneParent_House + Incomes:OneParent_House, 
                data = data_mod %>% 
                  filter(year == "2007") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_04 <- lm(Perc_LNP ~ . + Educ:MedianAge + CurrentlyStudying:RentLoan + Educ:OneParent_House + Incomes:OneParent_House, 
                data = data_mod %>% 
                  filter(year == "2004") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_01 <- lm(Perc_LNP ~ . + Educ:MedianAge + CurrentlyStudying:RentLoan + Educ:OneParent_House + Incomes:OneParent_House, 
                data = data_mod %>% 
                  filter(year == "2001") %>% 
                  select(Perc_LNP, (superset$varname %>% as.character)))
```

These models now have all main effects, plus the four interactions that were significant in at least half of the models. 


# Diagnostics
```{r}
aug_all <- bind_rows(augment(fit_ss_01) %>% mutate(year = "2001"), 
                     augment(fit_ss_04) %>% mutate(year = "2004"), 
                     augment(fit_ss_07) %>% mutate(year = "2007"), 
                     augment(fit_ss_10) %>% mutate(year = "2010"), 
                     augment(fit_ss_13) %>% mutate(year = "2013"), 
                     augment(fit_ss_16) %>% mutate(year = "2016"))
```

## Fitted values
```{r}
aug_all %>% 
  ggplot(aes(x=.fitted, y=Perc_LNP)) + 
  geom_abline(col = "blue") + 
  geom_point(alpha = 0.5) +
  facet_wrap(~year)
```


## Residual heteroskedasticity
```{r}
# Response vs fitted
aug_all %>% 
  ggplot(aes(x=.fitted, y=.resid)) + 
  geom_point() + geom_smooth() +
  facet_wrap(~year)
```

No signs of heteroskedasticity.

## Residual normality
```{r}
# Histogram
aug_all %>% 
  ggplot(aes(x = .resid)) + 
  geom_histogram() +
  facet_wrap(~year)

# QQ plots
aug_all %>% 
  ggplot(aes(sample = .resid)) + 
  geom_qq() + geom_qq_line() + 
  facet_wrap(~year)
```

Histograms don't look smooth.
Residuals look good.

## Non-linearities: Residuals against predictors
```{r}
aug_all %>%
  filter(year == "2016") %>% 
  gather(key = "variable", value = "value", -c(starts_with("."), Perc_LNP, year)) %>% 
  ggplot(aes(x = value, y = .resid)) +
  geom_point() + geom_smooth() + facet_wrap(~variable, scales = "free_x")
```

No obvious non-linearities in 2001, 2004, 2007, 2010, 2013, 2016.

## Residuals vs Predictors not in model
```{r}
vars_not_in <- names(data_mod)[which(!names(data_mod) %in% superset$varname)]

aug_all %>% bind_cols(data_mod %>% filter(!is.na(Perc_LNP))) %>% 
  filter(year == "2016") %>% 
  select(starts_with("."), c(vars_not_in), -c(Swing, year, Election_Division)) %>% 
  gather(key = "variable", value = "value", -c(starts_with("."), Perc_LNP)) %>%
  ggplot(aes(x = value, y = .resid)) +
  geom_point() + geom_smooth(level = 0.99) + facet_wrap(~variable, scales = "free")
```

No obvious patterns in the residuals vs omitted variables.

## Influence
```{r}
# Cook distance
aug_all %>% 
  ggplot(aes(x=.cooksd)) + geom_dotplot() + facet_wrap(~year)

aug_all %>% bind_cols(data_mod %>% filter(!is.na(Perc_LNP))) %>% select(-ends_with("1")) %>%  filter(.cooksd > 0.2)
```

Across the six elections, only Sydney in 2007 has high leverage (cook distance of 0.29). This is due to its strong support for Labor (69.5% of TPP vote), whilst having high RentLoan, NoReligion, Educ, CurrentlyStudying and Incomes. No other electorate in any year has cook distance greater than 0.2. Therefore there are no outliers that should be removed from the model. 
 
## Analysis

```{r}
# Extracting coefficients
ss_coef = data.frame(varname = names(fit_ss_01$coefficients),
                     year = as.character(rep(seq(2001, 2016, by = 3), 
                                             each = length(names(fit_ss_01$coefficients)))),
                     coef =
                       c(fit_ss_01$coefficients, 
                         fit_ss_04$coefficients, 
                         fit_ss_07$coefficients, 
                         fit_ss_10$coefficients, 
                         fit_ss_13$coefficients, 
                         fit_ss_16$coefficients))

# Point plot of coefficients for each variable, coloured by year
ss_coef %>% 
  filter(varname != "(Intercept)") %>% 
  ggplot(aes(x=varname, y=coef)) +
  geom_point(aes(col = year), size = 2.5, alpha = 0.8) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12))

```


# Plotting coefficients over time

The plot shows the significance (T test) of each variable, across years.

```{r}
## Create df of coefficients
library(broom)
all_coefs <- bind_rows(tidy(fit_ss_16) %>% mutate(year = "2016"), 
                       tidy(fit_ss_13) %>% mutate(year = "2013"), 
                       tidy(fit_ss_10) %>% mutate(year = "2010"), 
                       tidy(fit_ss_07) %>% mutate(year = "2007"), 
                       tidy(fit_ss_04) %>% mutate(year = "2004"), 
                       tidy(fit_ss_01) %>% mutate(year = "2001")) %>% 
  mutate(upper95 = estimate + 1.96*std.error, lower95 = estimate - 1.96*std.error)

# Plot 95% confidence intervals for each coefficient
all_coefs %>% 
  filter(term != "(Intercept)") %>% 
  ggplot(aes(x = year, y = estimate)) + 
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12))

save(all_coefs, file = "./Clean-Data/all_coefs.rda")

```


Or alternatively use an F test (drop1) to test significance.

```{r}
all_sig <- bind_rows(tidy(drop1(fit_ss_01, test = "F")) %>% mutate(year = "2001"),
                     tidy(drop1(fit_ss_04, test = "F")) %>% mutate(year = "2004"),
                     tidy(drop1(fit_ss_07, test = "F")) %>% mutate(year = "2007"),
                     tidy(drop1(fit_ss_10, test = "F")) %>% mutate(year = "2010"),
                     tidy(drop1(fit_ss_13, test = "F")) %>% mutate(year = "2013"),
                     tidy(drop1(fit_ss_16, test = "F")) %>% mutate(year = "2016")) %>% 
  rename(pval_F = p.value) %>% select(term, pval_F, year)

all_coefs_sig <- left_join(all_coefs, all_sig, by = c("term", "year"))                   

# Plot
all_coefs_sig %>% 
  filter(term != "(Intercept)") %>% 
  ggplot(aes(x = year, y = estimate)) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  geom_line(aes(group = term)) + 
  geom_point(aes(col = (pval_F < 0.05))) + 
  scale_color_manual(values = c("grey50", "magenta")) + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12))
```

# Comparing estimated effects with raw plots
If relationship appears to be the same, then variable is not masked by any of the others. If the relationship is not, then there is some dependence.

Go through variables one by one, and examine effects

### How coefficients change when we drop a variable
If the coefficient changes significantly, then there is some dependency
```{r}
drop_var <- function(fit) {
  dat <- fit$model
for (j in 2:ncol(dat)) {
  omitted_name <- names(dat)[j]
  dat_mod <- dat[, -j]
  mod <- lm(Perc_LNP ~ ., data = dat_mod)
  mod_out <- tidy(mod) %>% 
    mutate(omitted_var = omitted_name) %>% 
    left_join(tidy(fit) %>% select(term, estimate) %>% rename(full_estimate = estimate), by = "term") %>% 
    mutate(diff_estimate = full_estimate - estimate)
  
  if (j == 2) {
    mod_all <- mod_out
  } else {
    mod_all <- rbind(mod_all, mod_out)
  }
  
    
}
  
  mod_all <- mod_all %>% 
    arrange(-abs(diff_estimate)) %>% 
    filter(term != "(Intercept)")
  
  return(mod_all)
}


change_coef_16 <- drop_var(fit_ss_16) %>% mutate(year = "2016")
change_coef_13 <- drop_var(fit_ss_13) %>% mutate(year = "2013")
change_coef_10 <- drop_var(fit_ss_10) %>% mutate(year = "2010")
change_coef_07 <- drop_var(fit_ss_07) %>% mutate(year = "2007")
change_coef_04 <- drop_var(fit_ss_04) %>% mutate(year = "2004")
change_coef_01 <- drop_var(fit_ss_01) %>% mutate(year = "2001")

change_coef_all <- bind_rows(change_coef_16, change_coef_13, change_coef_10, change_coef_07, change_coef_04, change_coef_01) %>% mutate(lower95 = estimate - 1.96*std.error, upper95 = estimate + 1.96*std.error)

save(change_coef_all, file = "./Clean-Data/change_coef_all.rda")
```

### Born in South/Eastern Europe
```{r}
all_coefs %>% filter(term == "Born_SE_Europe") %>% 
  ggplot(aes(x=year, y=estimate)) + 
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against Born_SE_Europe
data_mod %>% ggplot(aes(x = Born_SE_Europe, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
```

Electorates with higher proportions of South or Eastern European populations are affiliated with support for Labor.

### Born in the UK
```{r}
all_coefs %>% filter(term == "Born_UK") %>% 
  ggplot(aes(x=year, y=estimate)) +
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against Born_SE_Europe
data_mod %>% ggplot(aes(x = Born_UK, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)

## Moore
aug_all %>% bind_cols(data_mod %>% filter(!is.na(Perc_LNP))) %>% select(-ends_with("1")) %>%  filter(Election_Division == "MOORE")

```

Electorates with higher proportions of people from the UK are affiliated with support for LNP across all years, however this is only significant in 2007 and 2010. The electorate Moore (WA) has the highest proportion of migrants from the UK, and has high leverage (.hat > 0.2 for all years). 

### Currently Studying
```{r}
all_coefs %>% filter(term == "CurrentlyStudying") %>% 
  ggplot(aes(x=year, y=estimate)) +
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against CurrentlyStudying
data_mod %>% ggplot(aes(x = CurrentlyStudying, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
```

Inspection of the raw data indicates that electoratres with more people currently studying should have an affiliation with the Labor party. This is also what we intuitively may expect, as Labor policies have been more favorable for students, often pitching more funding for eduaction than LNP. Our model indicates otherwise. In all but 2007 and 2010, after adjusting for other socio-demographics, the proportion of the population currently studying has no significant effect on party preference.

To test for confounding, we re-fit the model with dropping a single variable, and observe the change in coefficient for CurrentlyStudying. When omitting MedianAge, the coefficient decreases by a large amount, which is not surprising given these two are negatively correlated ($\rho = -0.683$). Similarly, the effect of omitting higher education levels is absorbed by CurrentlyStudying, causing a decrease in estimated coefficient. 


```{r}
change_coef_all %>% 
  filter(term == "CurrentlyStudying") %>% 
  ggplot(aes(x=omitted_var, y=estimate)) + 
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = full_estimate), col = "blue", linetype = 2, alpha = 0.7) + 
  geom_hline(aes(yintercept = 0), col = "grey50") + 
  facet_wrap(~year) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) 

cor(data_mod$MedianAge, data_mod$CurrentlyStudying)
```

### Educ
```{r}
all_coefs %>% filter(term == "Educ") %>% 
  ggplot(aes(x=year, y=estimate)) +
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against Educ
data_mod %>% ggplot(aes(x = CurrentlyStudying, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
```

Higher levels of education were associated with support for the Labor party in 2004 and 2007 elections, but were not significant in the others. We expected a significant effect in each election.

Omitting NoReligion results in a stronger estimated effect in support for Labor in 2010, 2013 and 2016.

```{r}
change_coef_all %>% 
  filter(term == "Educ") %>% 
  ggplot(aes(x=omitted_var, y=estimate)) + 
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = full_estimate), col = "blue", linetype = 2, alpha = 0.7) + 
  geom_hline(aes(yintercept = 0), col = "grey50") + 
  facet_wrap(~year) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) 
```

### Extractive
```{r}
all_coefs %>% filter(term == "Extractive") %>% 
  ggplot(aes(x=year, y=estimate)) +
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against Extractive
data_mod %>% ggplot(aes(x = Extractive, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
```

Our estimated effects are strongly positive each election, which matches our expectations based on the plots.


### Median Age
```{r}
all_coefs %>% filter(term == "MedianAge") %>% 
  ggplot(aes(x=year, y=estimate)) +
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against MedianAge
data_mod %>% ggplot(aes(x = MedianAge, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
```

Median age has a significantly positive relationship with support for LNP.

### Unemployed
```{r}
all_coefs %>% filter(term == "Unemployed") %>% 
  ggplot(aes(x=year, y=estimate)) +
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against Unemployed
data_mod %>% ggplot(aes(x = Unemployed, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
```

We expect there to be a strong relationship between Labor party support and high levels of unemployment, based on the raw data. The model indicates that this was true in 2001-2007, but in the previous three elections unemployment has not had a significant effect. Our initial conclusions are confounded by ManagerAdminClericalSales, MedianAge and OneParent_House. There is a negative correlation between ManagerAdminClericalSales ($\rho = 0.513$), meaning that areas with higher unemployment typically have less of the population working "office jobs", hence omitting this variable causes bias in our estimated of Unemployment. There is a strong positive correlation between Unemployment and OneParent_House ($\rho = 0.679$), indicating that initial conclusions may be confusing these effects.


```{r}
change_coef_all %>% 
  filter(term == "Unemployed") %>% 
  ggplot(aes(x=omitted_var, y=estimate)) + 
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = full_estimate), col = "blue", linetype = 2, alpha = 0.7) + 
  geom_hline(aes(yintercept = 0), col = "grey50") + 
  facet_wrap(~year) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) 

cor(data_mod$OneParent_House, data_mod$Unemployed)
```

### ManagerAdminClericalSales
```{r}
all_coefs %>% filter(term == "ManagerAdminClericalSales") %>% 
  ggplot(aes(x=year, y=estimate)) +
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against ManagerAdminClericalSales
data_mod %>% ggplot(aes(x = ManagerAdminClericalSales, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
```

Significantly positive relationship between ManagerAdminClericalSales and support for LNP across all years.

### NoReligion
```{r}
all_coefs %>% filter(term == "NoReligion") %>% 
  ggplot(aes(x=year, y=estimate)) +
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against NoReligion
data_mod %>% ggplot(aes(x = NoReligion, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
```

Negative effects estimated, but are only significant in 2010 and 2013. From the original plots we don't expect to see any significant relationship. 

```{r}
change_coef_all %>% 
  filter(term == "NoReligion") %>% 
  ggplot(aes(x=omitted_var, y=estimate)) + 
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = full_estimate), col = "blue", linetype = 2, alpha = 0.7) + 
  geom_hline(aes(yintercept = 0), col = "grey50") + 
  facet_wrap(~year) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) 

cor(data_mod$OneParent_House, data_mod$Unemployed)
```

### OneParent_House
```{r}
all_coefs %>% filter(term == "OneParent_House") %>% 
  ggplot(aes(x=year, y=estimate)) +
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against OneParent_House
data_mod %>% ggplot(aes(x = OneParent_House, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
```

Significantly negative relationship observed in original plots and estimated in model.

### OtherLanguageHome
```{r}
all_coefs %>% filter(term == "OtherLanguageHome") %>% 
  ggplot(aes(x=year, y=estimate)) +
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against OtherLanguageHome
data_mod %>% ggplot(aes(x = OtherLanguageHome, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
```

Model estimates insignificant effect, whereas the raw data indicates there should be a negative relationship. We see that if we omit Born_SE_Europe, its effect is absorbed into OtherLanguageHome. This is telling us that it does not matter about the language spoken, but rather where the population is born.

```{r}
change_coef_all %>% 
  filter(term == "OtherLanguageHome") %>% 
  ggplot(aes(x=omitted_var, y=estimate)) + 
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = full_estimate), col = "blue", linetype = 2, alpha = 0.7) + 
  geom_hline(aes(yintercept = 0), col = "grey50") + 
  facet_wrap(~year) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) 
```

### RentLoan
```{r}
all_coefs %>% filter(term == "RentLoan") %>% 
  ggplot(aes(x=year, y=estimate)) +
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + lims(y=c(-8,8))

## Voting against RentLoan
data_mod %>% ggplot(aes(x = RentLoan, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
```

Expect insignificant effect from the raw plots. In 2010 we see significant support for LNP.

```{r}
change_coef_all %>% 
  filter(term == "OtherLanguageHome") %>% 
  ggplot(aes(x=omitted_var, y=estimate)) + 
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = full_estimate), col = "blue", linetype = 2, alpha = 0.7) + 
  geom_hline(aes(yintercept = 0), col = "grey50") + 
  facet_wrap(~year) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) 
```





------------------------------------------------------------------------------------------

# Stories from the data

## Education and Students

Education policy has always been key policy issue in the weeks leading up to a federal election. The Labor party, more often than not, campaign with policies that boost funding for education, and the coalition will usually propose alternatives with less funding or aim to match particular objectives - for example, the "Better Schools Plan" in 2013. It would be reasonable to expect that electorates with higher education levels, and higher student populations, would be inclined to support Labor *every* election, which is what we observe in our primary plots. 

After adjusting for the other socio-demographics, we find that education levels are only related to support of the Labor party in the 2004 and 2007 elections, with other years being insignificant at the 5% level. If we omit the prevelence of atheism (NoReligion) from our model, the effect of education in favour of Labor increases to be significant in 2010 and 2013. The same is true for the proportion of people working in "extractive" jobs, in the same years. This indicates that our initial thoughts on the effect education levels would have is being confounded by these other factors. We are not laying any causal claims here, but rather indicating that our expectations about aggregate behaviour can be simeltaneously determined by grouping characteristics together. Essentially, our intuitions are very susceptible to omitted variable bias!

Similarly, we see higher student proportions being significantly related to increased Liberal support in 2007 and 2010. Omitting the age profile of the electorate (MedianAge) would lead to significant support for Labor in 2001, and would change our conclusions from significant to insignificant in 2007 and 2010. This is not surprising, as younger people are typically students, so higher student populations should mean lower median age, and these two are highly correlated ($\rho = -0.683$).

## Unemployment

Our model indicates that in the 2001, 2004 and 2007 elections, higher unemployment rates were linked with more support for the Labor party. Interestingly, in all of those elections the Liberal party was the incumbent party with John Howard as Prime Minister. From 2010 onwards, education has not had a significant effect, which is not what we would expect from the raw data plots. If we omit "office jobs", the estimated coefficient of unemployment becomes more negative, but remains insignificant in these three elections. Therefore, we conclude that the unemployment rate was a significant determinant in two-party preference for 2001, 2004 and 2007 elections, but has since become insignificant, after adjusting for other socio-demographics - contrary to expectations.

## Other Language at Home

From the Tampa affair in 2001, when John Howard diverted the MV Tampa to Nauru (carrying 400 Afghani refugees), to the "stop the boats" mantra of the 2013 election, the Liberal party have consistently campaigned on policies of stricter immigration. We expect electorates with high proportions of people speaking languages other than English at home to also have high proportions of migrants (correlation $\rho = 0.90$), so OtherLanguageHome should have a positive relationship with voting Labor - which we see in the raw plots. After accounting for (some) birthplace demographics, we find that language at home has no significant effect on two-party preference.


```{r}
load("~/Documents/R/Data/Clean/abs_all.rda")
abs_all <- abs_all %>% mutate(Born_Australia = 100 - Born_UK - Born_SE_Europe - Born_MidEast - Born_Asia - BornElsewhere) 

cor(abs_all$Born_Australia, abs_all$OtherLanguageHome)
cor(abs_all$Born_SE_Europe, abs_all$Born_Asia)
```

## Rental and Housing Loan Payments

In 2010, electorates with higher (median) rental prices and housing loan payments were significantly more likely to support the Liberal party. Although omitted from our model, the factor RentLoan has strong positive correlation with the Incomes factor ($\rho = 0.83$).

## Extractive

Even in the election before the mining boom began in 2002, areas with more people working in "extractive" industries (mining, gas, water, gas, waste, electricity and agriculture) were significantly more supportive of the coalition. Over the following two elections the two parties did not differ significantly in their policies on natural resources, and we our coefficient estimates do not change much relative to 2001 - remaining significantly positive.

In 2010, the Labor party proposed a 40% tax on "super profits" made from ‘the exploitation of Australia’s non-renewable resources’, which was heavily opposed by the Liberal party, who instead offered the Exploration Development Incentive. The mining sector, particularly in Western Australia, vehemently objected to Labor's policy, with Chamber of Minerals and Energy chief executive describing it as a "$\$9$ billion handbreak on the economy". Consequently, we see a huge jump in the effect of extractive jobs in 2010, with estimated coefficient increasing from $2.43$ to $5.63$ - becoming the largest coefficient in the model. Following the end of the mining boom in 2012, the estimated coefficient drops but remains significantly positive in 2013 and 2016.




