---
title: "Superset-Models"
author: "Jeremy Forbes"
date: "01/09/2018"
output: html_document
---

```{r}
library(tidyverse)
knitr::opts_knit$set(root.dir = "/Users/Jeremy/Documents/R/Modelling-Elections")
load("./Clean-Data/data_mod.rda")
load("./Clean-Data/var_imp_all.rda")
load("./Clean-Data/std_coef_all.rda")
```

# Supersets determined by Akaike weights


Choosing the top 5 from each year, create a superset.

```{r}
# Top 5 variables
superset_AW_vars <- var_imp_all %>% 
  group_by(year) %>% 
  top_n(n = 5, wt = sum_w) %>%
  ungroup() %>% 
  select(var, varname) %>% 
  unique()

#superset_AW_by_year <- var_imp_all %>% 
#  group_by(year) %>% 
#  top_n(n = 5, wt = sum_w) %>% 
#  arrange(-sum_w) %>% 
#  mutate(imp = 1:5)

```




# Supersets determined by Standardized Coefficients

Choosing the top 5 from each year, create a superset.

```{r}
# Top 6 variables
superset_SC_vars <- std_coef_all %>% 
  group_by(year) %>% 
  top_n(n = 5, wt = abs(avg_coef)) %>%
  ungroup() %>% 
  select(var, varname)  %>% 
  unique()

#superset_SC_by_year <- std_coef_all %>% 
#  group_by(year) %>% 
#  top_n(n = 5, wt = abs(avg_coef)) %>% 
#  select(var, avg_coef, varname, year) %>% 
#  arrange(-abs(avg_coef)) %>% 
#  mutate(imp = 1:5)
```

# Creating the super-set
Added Unemployment and OtherLanguageHome

```{r}
superset <- bind_rows(superset_AW_vars, superset_SC_vars) %>% group_by(varname) %>% unique()
```



Run a regression each year using this superset

```{r}
fit_ss_16 <- lm(Perc_LNP ~ ., 
                data = data_mod %>% 
                  filter(year == "2016") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_13 <- lm(Perc_LNP ~ ., 
                data = data_mod %>% 
                  filter(year == "2013") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_10 <- lm(Perc_LNP ~ ., 
                data = data_mod %>% 
                  filter(year == "2010") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_07 <- lm(Perc_LNP ~ ., 
                data = data_mod %>% 
                  filter(year == "2007") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_04 <- lm(Perc_LNP ~ ., 
                data = data_mod %>% 
                  filter(year == "2004") %>% 
                  select(Perc_LNP,  (superset$varname %>% as.character)))

fit_ss_01 <- lm(Perc_LNP ~ ., 
                data = data_mod %>% 
                  filter(year == "2001") %>% 
                  select(Perc_LNP, (superset$varname %>% as.character)))

# Extracting coefficients
ss_coef = data.frame(varname = names(fit_ss_01$coefficients),
                     year = as.character(rep(seq(2001, 2016, by = 3), 
                                             each = length(names(fit_ss_01$coefficients)))),
                     coef =
                       c(fit_ss_01$coefficients, 
                         fit_ss_04$coefficients, 
                         fit_ss_07$coefficients, 
                         fit_ss_10$coefficients, 
                         fit_ss_13$coefficients, 
                         fit_ss_16$coefficients))

# Plot
ss_coef %>% 
  filter(varname != "(Intercept)") %>% 
  ggplot(aes(x=varname, y=coef)) +
  geom_point(aes(col = year), size = 2.5, alpha = 0.8) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12))

```

# Plotting coefficients over time
```{r}
## Create df of coefficients
library(broom)
all_coefs <- bind_rows(tidy(fit_ss_16) %>% mutate(year = "2016"), 
                       tidy(fit_ss_13) %>% mutate(year = "2013"), 
                       tidy(fit_ss_10) %>% mutate(year = "2010"), 
                       tidy(fit_ss_07) %>% mutate(year = "2007"), 
                       tidy(fit_ss_04) %>% mutate(year = "2004"), 
                       tidy(fit_ss_01) %>% mutate(year = "2001")) %>% 
  mutate(upper95 = estimate + 1.96*std.error, lower95 = estimate - 1.96*std.error)

# Plot
all_coefs %>% 
  filter(term != "(Intercept)") %>% 
  ggplot(aes(x = year, y = estimate)) + 
  geom_point() + geom_errorbar(aes(ymin = lower95, ymax = upper95), width = 0.25) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  facet_wrap(~term)
```

The plot above shows the significance (T test) of each variable, across years.


# Checking which are significant (F test)
```{r}
all_sig <- bind_rows(tidy(drop1(fit_ss_01, test = "F")) %>% mutate(year = "2001"),
                     tidy(drop1(fit_ss_04, test = "F")) %>% mutate(year = "2004"),
                     tidy(drop1(fit_ss_07, test = "F")) %>% mutate(year = "2007"),
                     tidy(drop1(fit_ss_10, test = "F")) %>% mutate(year = "2010"),
                     tidy(drop1(fit_ss_13, test = "F")) %>% mutate(year = "2013"),
                     tidy(drop1(fit_ss_16, test = "F")) %>% mutate(year = "2016")) %>% 
  rename(pval_F = p.value) %>% select(term, pval_F, year)

all_coefs_sig <- left_join(all_coefs, all_sig, by = c("term", "year"))                   

# Plot
all_coefs_sig %>% 
  filter(term != "(Intercept)") %>% 
  ggplot(aes(x = year, y = estimate)) + 
  geom_hline(aes(yintercept = 0), alpha = 0.5) + 
  geom_line(aes(group = term)) + 
  geom_point(aes(col = (pval_F < 0.05))) + 
  scale_color_manual(values = c("grey50", "magenta")) + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12))
```

# Confirm that these match our initial thoughts


```{r}
## Voting against Born_SE_Europe
data_mod %>% ggplot(aes(x = Born_SE_Europe, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)

## Voting against Born_UK
data_mod %>% ggplot(aes(x = Born_UK, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
  
## Voting against CurrentlyStudying
data_mod %>% ggplot(aes(x = CurrentlyStudying, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
      
## Voting against Educ
data_mod %>% ggplot(aes(x = Educ, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
  
## Voting against Extractive
data_mod %>% ggplot(aes(x = Extractive, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)
  
## Voting against Unemployed
data_mod %>% ggplot(aes(x = Unemployed, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)

## Voting against LFRet
data_mod %>% ggplot(aes(x = MedianAge, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)

## Voting against ManagerAdminClericalSales
data_mod %>% ggplot(aes(x = ManagerAdminClericalSales, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)

## Voting against NoReligion
data_mod %>% ggplot(aes(x = NoReligion, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)

## Voting against OneParent_House
data_mod %>% ggplot(aes(x = OneParent_House, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)

## Voting against OtherLanguageHome
data_mod %>% ggplot(aes(x = OtherLanguageHome, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)

## Voting against RentLoan
data_mod %>% ggplot(aes(x = RentLoan, y = Perc_LNP)) + geom_point(aes(label = Election_Division)) + geom_smooth(method = "lm") + facet_wrap(~year)



data_mod %>% filter(Perc_LNP > 55) %>% ggplot(aes(x = year, y = Unemployed)) + geom_line(aes(group = Election_Division, label = Election_Division))
```

Born_SE_Europe: Each year, electorates with higher proportions of people born in South and Eastern Europe are  more attracted to the Labor party. This fits with our initial inspection of the data.

Born_UK: In only the 2007 and 2010 elections, proportion of people born in the UK was significantly influential in electorate preference, with higher proportions being more associated with the Liberal party. The sign of the relationship does not change over the elections.

CurrentlyStudying: This result contradicts our expectations entirely, as we expected electorates with larger student demographics to have more affiliation with the Labor party. 

Educ: We expected areas with higher education levels to support Labor, which is the effect produced by the models. Throughout 2004-2013, this effect was particularly strong.

Extractive: Electorates with more jobs in agriculture, mining, electricity, gas, water or waste, are strongly affiliated with the coalition. We see a huge spike in effect in 2010, which corresponds with the peak of the mining boom. The consistently strong levels of support are rational, because the Liberal party has policies that favour these industries. 

Incomes: Areas with higher incomes should have a preference for the Liberal party, due to their tax policies being lighter on higher income brackets. We see that in 2001-2007, higher income areas were particularly strong in their support for the Liberal party, but from 2010, this positive effect has weakened.

LFRet: Matches - to be removed.

ManagerAdminClericalSales: Matches

NoReligion: No relationship appears in basic plots, but we expect electorates with more identifying athiests to be more associated with the Labor party, as it is seen as being more socially progressive. We find that from 2010 onwards, this became apparent. What changed in atheist attitudes over time?

OneParent_House: We expect areas with higher proportions of single parent families to be more supportive of Labor. Labor's policies usually are geared towards family benefits and related issues that would be important for areas with high incidence of single parent families. The model shows a consistently strong relationship with Labor support over the years.

OtherLanguageHome: We don't expect this to have any significant effect on two party preferred vote, and the model confirms this. There is only a weak affiliation with the Liberal party, although not significant. Original plots indicate that we should see support for Labor.

RentLoan: Labor policy in 2007 triggered increase in support for Labor, which changed drastically in 2010 - perhaps something to do with negative gearing?








## How coefficients change when we drop a variable
If the coefficient changes significantly, then there is some dependency
```{r}
drop_var <- function(fit) {
  dat <- fit$model
for (j in 2:ncol(dat)) {
  omitted_name <- names(dat)[j]
  dat_mod <- dat[, -j]
  mod <- lm(Perc_LNP ~ ., data = dat_mod)
  mod_out <- tidy(mod) %>% 
    mutate(omitted_var = omitted_name) %>% 
    left_join(tidy(fit) %>% select(term, estimate) %>% rename(full_estimate = estimate), by = "term") %>% 
    mutate(diff_estimate = full_estimate - estimate)
  
  if (j == 2) {
    mod_all <- mod_out
  } else {
    mod_all <- rbind(mod_all, mod_out)
  }
  
    
}
  
  mod_all <- mod_all %>% 
    arrange(-abs(diff_estimate)) %>% 
    filter(term != "(Intercept)")
  
  return(mod_all)
}


change_coef_16 <- drop_var(fit_ss_16) %>% mutate(year = "2016")
change_coef_13 <- drop_var(fit_ss_13) %>% mutate(year = "2013")
change_coef_10 <- drop_var(fit_ss_10) %>% mutate(year = "2010")
change_coef_07 <- drop_var(fit_ss_07) %>% mutate(year = "2007")
change_coef_04 <- drop_var(fit_ss_04) %>% mutate(year = "2004")
change_coef_01 <- drop_var(fit_ss_01) %>% mutate(year = "2001")

bind_rows(change_coef_16, change_coef_13, change_coef_10, change_coef_07, change_coef_04, change_coef_01) %>% 
  arrange(-abs(diff_estimate)) %>% 
  ggplot(aes(x=omitted_var, y=diff_estimate)) + geom_point(aes(col = year)) + facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12))

change_coef_16 %>% 
  gather(key = "Type", value = "Estimate", -c(term, std.error, statistic, p.value, omitted_var, diff_estimate, year)) %>%
  ggplot(aes(x=omitted_var, y=Estimate)) + geom_point(aes(col = factor(Type))) + facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12))

# Matrix scatterplot
pairs(data_mod %>% filter(year == 
    "2016") %>% select(superset$varname %>% as.character))
```


### Adding interactions
Record p-value for F test adding a single interaction to each model
```{r}
fit = fit_ss_16

interact_F <- function(fit) {
  data_mod <- fit$model
  x_names <- names(data_mod)[which(names(data_mod) != "Perc_LNP")]
  
  pvalues_F <- matrix(nrow = length(x_names), ncol = length(x_names)) %>% as.data.frame()
  colnames(pvalues_F) <- x_names
  
  pvalues_F <- pvalues_F %>% 
    mutate(interact_var1 = x_names)
  

  for (i in 1:length(x_names)) {
    
    for (j in 1:length(x_names)) {
      
      if (i > j) {
      formula = paste0(
        paste0(
        paste0("Perc_LNP ~ . + ", x_names[i]), ":"), x_names[j])
      
      mod <- lm(formula, data_mod)
      
      suppressWarnings(tidy_drop <- tidy(drop1(mod, test = "F")))
    
      pval = tidy_drop$p.value[grep(":", tidy_drop$term)]
      
      pvalues_F[i,j] <- pval
      
      }
      
    }
    
  }
  
  pvalues_F <- pvalues_F %>% 
    gather(key = "interact_var2", value = "pvalue", -interact_var1) %>% 
    filter(!is.na(pvalue))
  
  return(pvalues_F)
}

int16 <- interact_F(fit_ss_16) %>% mutate(year = "2016")
int13 <- interact_F(fit_ss_13) %>% mutate(year = "2013") 
int10 <- interact_F(fit_ss_10) %>% mutate(year = "2010") 
int07 <- interact_F(fit_ss_07) %>% mutate(year = "2007") 
int04 <- interact_F(fit_ss_04) %>% mutate(year = "2004") 
int01 <- interact_F(fit_ss_01) %>% mutate(year = "2001") 

bind_rows(int01, int04, int07, int10, int13, int16) %>% 
  filter(pvalue < 0.001) %>% 
  group_by(interact_var1, interact_var2) %>% 
  summarise(n = n()) %>% View


```



Born_SE_Europe
- Doesn't appear to be strongly dependent on any of the other variables

Born_UK
- No strong dependencies

CurrentlyStudying
- Affected by MedianAge

Education
- Most variables

Extractive
- Relatively unaffected

ManageAdminClericalSales
- Nothing strong

Median Age
- Currently studying, but not strong

No Religion
- ManagerAdminClericalSales but not strong

OneParent_House
- Extractive large dependency
- Unemployed also strong, and changing effect

OtherLanguageHome
- Born_SE_Europe is huge
- Small dependence with MedianAge and NoReligion

RentLoan
- Strongly dependent on Extractive
- Moderate dependence with Educ and NoReligion

Unemployed
- Strong with ManagerAdminClericalSales
- Moderatew ith MedianAge and OneParent_House

I would suggest adding interactions:
- Born_SE_Europe and OtherLanguageHome
- Educ and ManagerAdminClericalSales
- Educ and NoReligion
- OneParent_House and Extractive
- RentLoan and Extractive
- Unemployed and ManagerAdminClericalSales
- Unemployed and MedianAge
- 


To check the sensitivity of our estimates to omitted variable bias, we observe the change in coefficients when adding to the model a single unused predictor. We see that OtherLanguageHome is highly endogenous, mostly due to its correlation with the omitted regions of birth, and religions. Education is also strongly affected by the omitted job industries. 


## Comparison with single variable regressions
```{r}
onevar_coef <- rbind(oneway_2001 %>% unnest %>% select(vars, coef) %>% mutate(year = "2001"),
                     oneway_2004 %>% unnest %>% select(vars, coef) %>% mutate(year = "2004"),
                     oneway_2007 %>% unnest %>% select(vars, coef) %>% mutate(year = "2007"),
                     oneway_2010 %>% unnest %>% select(vars, coef) %>% mutate(year = "2010"),
                     oneway_2013 %>% unnest %>% select(vars, coef) %>% mutate(year = "2013"),
                     oneway_2016 %>% unnest %>% select(vars, coef) %>% mutate(year = "2016")) %>% 
  rename(var = vars) %>% 
  left_join(name_vars, by = "var") %>% mutate(Type = "SingleVarReg") %>% select(-var)

rbind(onevar_coef, ss_coef %>% mutate(Type = "Superset")) %>% 
  filter(varname != "(Intercept)", varname %in% ss_coef$varname) %>% 
  ggplot(aes(x = varname, y = coef)) + 
  geom_line(aes(group = varname)) + 
  geom_point(aes(col = Type)) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12)) + facet_wrap(~year)
```

We compare the standardized coefficients from the superset model to those from the single variable regressions to demonstrate the problem of drawing insights from single variable regressions. Single variable regressions are used in previous sociodemographic analyses of Australian federal elections (@StimsonALLPAPERS), but no extensions to include multiple regressors have been previously explored.

In at least one election year, we find that single variable regressions estimate the effects of CurrentlyStudying, NoReligion, Transformative, MedianAge and RentLoan to have mistaken party associations. CurrentlyStudying, RentLoan and Transfomrative would be estimated to have a positive relationships with support for Labor, but once we have appropriately adjusted for other factors (in multiple regression), the relationship moves in support of Liberal. Conversely, higher NoReligion and MedianAge would be said to support Liberal, but adjusting for other factors, either support Labor or are insignificant.


## Effect over time

```{r}
# Split over two plots
ss_AW_coef %>% 
  filter(varname != "(Intercept)") %>% 
  filter(varname %in% unique(ss_AW_coef$varname)[1:7]) %>% 
  ggplot(aes(x = as.numeric(year), y = coef)) + geom_point(aes(col = varname)) + geom_line(aes(col=varname))

ss_AW_coef %>% 
  filter(varname != "(Intercept)") %>% 
  filter(!varname %in% unique(ss_AW_coef$varname)[1:7]) %>% 
  ggplot(aes(x = as.numeric(year), y = coef)) + geom_point(aes(col = varname)) + geom_line(aes(col=varname))
```

**Unchanging**
Born_SE_Europe: Consistenty strong labor support, although effect has slightly reduced over the years.
ManagerClericalAdminSales: Always strong support for Liberal. Small peak in 2007. Drop in 2010 and on upwards trend.
Education: relatively insignificant, unchanged over years. 
Christians other than Anglican and Catholic: spike for Liberal support in 2010

**More Changes**
OneParent_House: Consistent labor support, but dropped in 2010. Increased again 2013, 2016.
LFRet: 2001 was insignificant, but has become more supportive of Labor. *Superannuation reform*
Extractive: Always been highly supportive of Liberal. Huge spike in 2010, slight drop in 2013 and fixed 2016. *Mining boom* finished in 2011, and peaked in ???.
RentLoan: Little or no effect before 2010, when support spiked for Liberal. Has held here over past two elections.
BornUK: Spike in 2007, steady downwards trend afterwards.
CurrentlyStudying: Initially supportive of Labor, but steep upwards trend towards Liberal over 2004-2010. Drop over last elecitons.
MedianAge: Liberal in 2004, Labor 2007, Liberal 2010, then strong movements towards Labor.
NoReligion: Always more associated with Labor. 2010 election big spike towards Labor. Now moving back towards zero - but this could also be due to more people identifying as Labor.
Transformative: Spike for Liberal in 2004, drop in 2007, steady increase since.




## Omitted variable bias

```{r}
fit = fit_ss_01
Year = 2001

OVB <- function(fit, data_mod, Year) {
  data_fit <- fit$model
  
  data_om <- data_mod %>% 
    filter(year == as.character(Year), !is.na(Perc_LNP)) %>% 
    select(-c(names(data_fit), year, Swing, Election_Division))
  
for (j in 1:ncol(data_om)) {
  omitted_name <- names(data_om)[j]
  
  data_use <- bind_cols(data_fit, data_om %>% select(omitted_name))
  
  mod <- lm(Perc_LNP ~ ., data = data_use)
  
  mod_out <- tidy(mod) %>% 
    mutate(omitted_var = omitted_name) %>% 
    right_join(tidy(fit) %>% select(term, estimate) %>% rename(full_estimate = estimate), by = "term") %>% 
    mutate(diff_estimate = full_estimate - estimate)
  
  if (j == 1) {
    mod_all <- mod_out
  } else {
    mod_all <- rbind(mod_all, mod_out)
  }
  
    
}
  
  mod_all <- mod_all %>% 
    arrange(-abs(diff_estimate)) %>% 
    filter(term != "(Intercept)") %>% 
    mutate(year = as.character(Year))
  
  return(mod_all)
}

omitted_var_bias <- bind_rows(omitted_var_bias_16 <- OVB(fit_ss_16, data_mod, 2016),
                              omitted_var_bias_13 <- OVB(fit_ss_13, data_mod, 2013),
                              omitted_var_bias_10 <- OVB(fit_ss_10, data_mod, 2010),
                              omitted_var_bias_07 <- OVB(fit_ss_07, data_mod, 2007),
                              omitted_var_bias_04 <- OVB(fit_ss_04, data_mod, 2004),
                              omitted_var_bias_01 <- OVB(fit_ss_01, data_mod, 2001))

# Plot to see which variables are affected by OVB
omitted_var_bias %>% 
  ggplot(aes(x = omitted_var, y = diff_estimate)) + 
  geom_point(aes(col = year), alpha = 0.8) +
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 12))
```